---
title: "ATTACHOT_DATA607SP2018_Assignment3"
author: "Go Attachot"
date: "2/18/2018"
output: html_document
---

#### WEERAPAT (GO) ATTACHOT
#### CUNY SPS, SPRING 2018, DATA 607
#### Assignment 3, R Character Manipulation and Date Processing
#### February 18, 2018

# Problem 3: Copy the introductory example.  The vector name stores the extracted names
### Data preparation: Read the raw data provided into R
```{r}
library(readr)
library(stringr)
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
```

### Extract names from the raw data and keep them in vector name as specify by the question
```{r}
name <- unlist(str_extract_all(raw.data, "[[:alpha:],. ]{2,}"))
name
```

## Question 1: Use the tools of this chapter to rearrange the vector so that all elements conform to the standard first_name last_name
```{r}
# Reformat the names that are not in the format we need
namewithcomma <- str_split(name, ", ", simplify = TRUE)
FName_LName <- str_c(namewithcomma[, 2], namewithcomma[, 1])
FName_LName <- str_replace(FName_LName, "([a-z])([A-Z])", "\\1 \\2")
```
```{r}
# Now we have the names in the First Name and Last Name order (but still with the title)
FName_LName
```
```{r}
# Additional modification to remove the title from all names
Q3.1NameNoTitle <- str_replace(FName_LName, "[[:alpha:]]{2,}\\. ", "")
```
```{r}
# Display the names as required by the question
Q3.1NameNoTitle
```

## Question 2: Construct a logical vector indicating whether a character has a title (i.e., Rev. and Dr.)
```{r}
Q3.2CheckForTitle <- str_detect(FName_LName, "[[:alpha:]]{2,}\\.")
```
```{r}
# Result for Question 2
Q3.2CheckForTitle
```

## Question 3: Construct a logical vector indicating whether a character has a second name
```{r}
Q3.3CheckForSecondName <- str_detect(name, " [A-z]{1,}\\. ")
```
```{r}
# Result for Question 3
Q3.3CheckForSecondName
```

# Problem 4: Describe the types of strings that conform to the following regular expressions and construct an example that is matched by the regular expression

## Question 1: [0-9]+\\$
#### A string contains at least one digit of number between 0 and 9 followed by "$"
```{r}
# Example of string extraction for Question 1
str_extract_all("My tuition at CUNY SPS this semester is US2,740$", "[0-9]+\\$")
```

## Question 2: \\b[a-z]{1,4}\\b
#### A string contains between one and four lowercase characters (a to z)
```{r}
# Example of string extraction for Question 2
str_extract_all("My tuition at CUNY SPS this semester is US2,740$", "\\b[a-z]{1,4}\\b")
```

## Question 3: .*?\\.txt$
#### A string contains any type of number or character of any length that is esstentially a name of a text file (.txt)
```{r}
# Example of string extraction for Question 3
str_extract_all("A file I used yesterday was CUNYSPS.txt", ".*?\\.txt$")
```

## Question 4: \\d{2}/\\d{2}/\\d{4}
#### A string contains a total of eight (8) digits of number in the format similar to month/date/year or date/month/year e.g. 13/01/2018 or 01/20/2018
```{r}
# Example of string extraction for Question 4
str_extract_all("My dog was born on 01/12/2009", "\\d{2}/\\d{2}/\\d{4}")
```

## Question 5: <(.+?)>.+?</\\1>
#### A string contains a set of characters similar to HTML codes with <...> XXX </...> format.  The string search will look for a set of characters enclosed between <...> and </...> format.
```{r}
# Example of string extraction for Question 5
str_extract_all("A sample of HTML code I learn is <head>TEST_TEST_TEST</head>", "<(.+?)>.+?</\\1>")
```

# Problem 9: The following code hides a secret message.  Crack it with R and regular expressions.  Hint: Some of the characters are more revealing than others!  The code snippet is also available in the materials at www.r-datacllection.com
### Data preparation: Read the secret code provided into R
```{r}
Q9SecretCode <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"
```

#### I can notice an uppercase letter hidden among these mass of texts so this is what I will try
```{r}
hiddenmessage <- str_extract_all(Q9SecretCode, "[:upper:]|[:punct:]")
unlist(hiddenmessage)
```

