---
title: "ATTACHOT_DATA607SP2018_Assignment4"
author: "Go Attachot"
date: "3/4/2018"
output:
  html_document: default
  pdf_document: default
---

#### WEERAPAT (GO) ATTACHOT
#### CUNY SPS, SPRING 2018, DATA 607
#### Assignment 4, Tidying and Transforming Data
#### March 4, 2018

### Data preparation: Load necessary packages and read the CSV file into R
```{r}
library(stringr)
library(dplyr)
library(knitr)
library(tidyr)
rawdata <- read.csv("ATTACHOT_DataForAssignment4.csv", header = FALSE, sep = ",", stringsAsFactors = FALSE)
head(rawdata)
```

### Recreate the column and row names to get data ready for analyses.
```{r}
rawdata$V1[1] <- "Airline"
rawdata$V2[1] <- "Flight Status"
head(rawdata)
names(rawdata) <- rawdata[1,]
rawdata <- rawdata[-c(1),]
rawdata <- rawdata[-c(3),]
rawdata$Airline[2] <- "ALASKA"
rawdata$Airline[4] <- "AM WEST"
```

### Playing with tools from package tidyr to essentially transpose the data
```{r}
rawdata_format1 <- rawdata %>% gather ("Airport", "Number of Flights", 3:7)
rawdata_format2 <- rawdata_format1 %>% spread(`Flight Status`, `Number of Flights`)
FinalData <- rawdata_format2
head(FinalData)
```

### Sorry I am running out of time.  I would submit the small analyses if you want to see it.
