---
title: "ATTACHOT_DATA607SP2018_Assignment1"
author: "Go Attachot"
date: "2/4/2018"
output: html_document
---

#### WEERAPAT (GO) ATTACHOT
#### CUNY SPS, SPRING 2018, DATA 607
#### Assignment 1, Loading Data into a Data Frame
#### February 4, 2018

# About the Data

### Citation: Mushroom records drawn from The Audubon Society Field Guide to North American Mushrooms (1981). G. H. Lincoff (Pres.), New York: Alfred A. Knopf.

# Data preparation: Read full dataset in to R and display the dataset
``` {r}
library(readr)
library(RCurl)
library(plyr)
Mushroom <- read.csv("http://raw.github.com/aweerapat/DATA607SP2018/master/Mushroom.csv", header = FALSE)
names(Mushroom) <- c("classes", "cap-shape", "cap-surface", "cap-color", "bruises", "odor", "gill-attachment", "gill-spacing", "gill-size", "gill-color", "stalk-shape", "stalk-root", "stalk-surface-above-ring", "stalk-surface-below-ring", "stalk-color-above-ring", "stalk-color-below-ring", "veil-type", "veil-color", "ring-number", "ring-type", "spore-print-color", "population", "habitat")
```
``` {r}
head(Mushroom)
```

# Choose five (5) columns and update data type so that the original one-letter code can be converted to a full-text explanation.
``` {r}
Mushroom$classes <- as.character(Mushroom$classes)
Mushroom$`cap-shape` <- as.character(Mushroom$`cap-shape`)
Mushroom$bruises <- as.character(Mushroom$bruises)
Mushroom$`veil-color` <- as.character(Mushroom$`veil-color`)
Mushroom$habitat <- as.character(Mushroom$habitat)
```

# Replace the abbreviations in the five columns chosen with the full descriptions, as outlined in the data dictionary.
``` {r}
Mushroom$classes[Mushroom$classes == "e"] <- "Edible"
Mushroom$classes[Mushroom$classes == "p"] <- "Poisonous"
Mushroom$`cap-shape`[Mushroom$`cap-shape` == "b"] <- "bell"
Mushroom$`cap-shape`[Mushroom$`cap-shape` == "c"] <- "conical"
Mushroom$`cap-shape`[Mushroom$`cap-shape` == "x"] <- "convex"
Mushroom$`cap-shape`[Mushroom$`cap-shape` == "f"] <- "flat"
Mushroom$`cap-shape`[Mushroom$`cap-shape` == "k"] <- "knobbed"
Mushroom$`cap-shape`[Mushroom$`cap-shape` == "s"] <- "sunken"
Mushroom$bruises[Mushroom$bruises == "t"] <- "bruises"
Mushroom$bruises[Mushroom$bruises == "f"] <- "no-bruises"
Mushroom$`veil-color`[Mushroom$`veil-color` == "n"] <- "brown"
Mushroom$`veil-color`[Mushroom$`veil-color` == "o"] <- "orange"
Mushroom$`veil-color`[Mushroom$`veil-color` == "w"] <- "white"
Mushroom$`veil-color`[Mushroom$`veil-color` == "y"] <- "yellow"
Mushroom$habitat[Mushroom$habitat == "g"] <- "grasses"
Mushroom$habitat[Mushroom$habitat == "l"] <- "leaves"
Mushroom$habitat[Mushroom$habitat == "m"] <- "meadows"
Mushroom$habitat[Mushroom$habitat == "p"] <- "paths"
Mushroom$habitat[Mushroom$habitat == "u"] <- "urban"
Mushroom$habitat[Mushroom$habitat == "w"] <- "waste"
Mushroom$habitat[Mushroom$habitat == "d"] <- "woods"
```

# Create a data frame containing a subset of the main dataset.  This data frame contains 5 columns and the first 50 lines of the dataset.
``` {r}
Mushroom.DataFrame <- data.frame(Mushroom[(1:50), c(1, 2, 5, 18, 23)])
```

# Display a data frame to confirm that the desire results are created.
``` {r}
head(Mushroom.DataFrame)
View(Mushroom.DataFrame)
```